Improved Particle Approximations \\ to the Joint Smoothing Distribution \\ Using Markov Chain Monte Carlo

### 2012-02-15 Paper/draft4_MCMCsmoother.tex
Rewriting draft.

%% Packages
\usepackage{cite}
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  \graphicspath{{../pdf/}{../jpeg/}}
  \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  \usepackage[dvips]{graphicx}
  \graphicspath{{../eps/}}
  \DeclareGraphicsExtensions{.eps}
\fi
\usepackage[cmex10]{amsmath}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{array}
\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{eqparbox}
\usepackage[font=footnotesize]{subfig}
\usepackage{fixltx2e}
\usepackage{stfloats}
\usepackage{url}

@@

% The paper headers
\markboth{IEEE Transaction in Signal Processing,~Vol.~1, No.~1, January~1901}%
{Shell \MakeLowercase{\textit{et al.}}: Particle smoothing using Markov chain Monte Carlo sampling for backwards simulation}

@@

\begin{IEEEeqnarray}{rCl}
p(x_{1:k}|\tilde{x}_{k+1}, y_{1:K}) & =       & p(x_{1:k}|\tilde{x}_{k+1}, y_{1:k}) \nonumber \\
                                    & \propto & p(\tilde{x}_{k+1}|x_k) p(x_k|x_{k-1}) p(y_k|x_x) p(x_{1:k}|y_{1:k-1})
\end{IEEEeqnarray}

@@

\begin{IEEEeqnarray}{rCl}
\underbrace{\begin{bmatrix}x_k \\ y_k \\ \dot{x}_k \\ \dot{y}_k\end{bmatrix}}_{\mathbf{x}_k} &=& \underbrace{\begin{bmatrix}I_2 & \Delta t I_2 \\ 0_2 & I_2\end{bmatrix}}_{\mathbf{A}} \underbrace{\begin{bmatrix}x_{k-1} \\ y_{k-1} \\ \dot{x}_{k-1} \\ \dot{y}_{k-1}\end{bmatrix}}_{\mathbf{x}_{k-1}} + \underbrace{\begin{bmatrix}w_{1,k} \\ w_{2,k} \\ w_{3,k} \\ w_{4,k}\end{bmatrix}}_{\mathbf{w}_k} \\
\underbrace{\begin{bmatrix}b_k \\ r_x\end{bmatrix}}_{\mathbf{y}_k} &=& \begin{bmatrix}\tan^{-1}(y_k / x_k) \\ \sqrt{x_k^2+y_k^2} \end{bmatrix} + \underbrace{\begin{bmatrix}v_{1,k} \\ v_{2,k}\end{bmatrix}}_{\mathbf{v}_k} \\
\end{IEEEeqnarray}

@@

\begin{figure}
\centerline{\subfloat[Case 1]{\includegraphics[width=0.45\columnwidth]{case1_trajectory-crop.pdf}%
\label{fig_first_case}}
\hfil
\subfloat[Case 2]{\includegraphics[width=0.45\columnwidth]{case2_trajectory-crop.pdf}%
\label{fig_second_case}}}
\caption{Example trajectory with observations from the two parameter cases.}
\label{fig:example_trajectories}
\end{figure}

@@

\begin{table}%
\begin{tabular}{|c||c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{1cm} Postion RMSE \end{minipage} & \begin{minipage}[c]{1cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{1cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{1cm}  Unique Particles \end{minipage} \\
\hline
FS 						& 0.578 & 0.968 & 0 & 2.25 \\
DBRS					& 0.475 & 0.762 & 122 & 20.3 \\
\hline
MCMC-BRS (1)	& 0.509 & 0.823 & 3 & 13.7 \\
MCMC-BRS (3)	& 0.493 & 0.790 & 7 & 17.4 \\
MCMC-BRS (10)	& 0.482 & 0.768 & 21 & 19.6 \\
MCMC-BRS (30)	& 0.480 & 0.761 & 62 & 20.2 \\
MCMC-BRS (100)& 0.476 & 0.764 & 202 & 20.4 \\
\hline
MCMC-BSS (1)	& 0.473 & 0.758 & 14 & 44.3 \\
MCMC-BSS (3)	& 0.461 & 0.734 & 29 & 69.7 \\
MCMC-BSS (10)	& 0.451 & 0.720 & 82 & 89.8 \\
MCMC-BSS (30)	& 0.444 & 0.713 & 232 & 96.7 \\
MCMC-BSS (100)& 0.443 & 0.709 & 755 & 98.6 \\
\hline
\end{tabular}
\caption{Smoother performance measures for parameter case 1. All results are averaged over 10 runs, with 500 time steps in each run.}
\label{tab:case1_performance}
\end{table}

\begin{table}%
\begin{tabular}{|c||c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{1cm} Postion RMSE \end{minipage} & \begin{minipage}[c]{1cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{1cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{1cm}  Unique Particles \end{minipage} \\
\hline
FS 						& 0. & 0. & 0 &  \\
DBRS					& 0. & 0. &  &  \\
\hline
MCMC-BRS (1)	& 0. & 0. &  &  \\
MCMC-BRS (3)	& 0. & 0. &  &  \\
MCMC-BRS (10)	& 0. & 0. &  &  \\
MCMC-BRS (30)	& 0. & 0. &  &  \\
MCMC-BRS (100)& 0. & 0. &  &  \\
\hline
MCMC-BSS (1)	& 0. & 0. &  &  \\
MCMC-BSS (3)	& 0. & 0. &  &  \\
MCMC-BSS (10)	& 0. & 0. &  &  \\
MCMC-BSS (30)	& 0. & 0. &  &  \\
MCMC-BSS (100)& 0. & 0. &  &  \\
\hline
\end{tabular}
\caption{Smoother performance measures for parameter case 2. All results are averaged over 10 runs, with 500 time steps in each run.}
\label{tab:case2_performance}
\end{table}

\begin{figure}%
\includegraphics[width=\columnwidth]{case1_smoother_comparison_posRMSE_time-crop.pdf}%
\caption{RMSEs and running times of various smoothing algorithms}%
\label{fig:case1_rmse_vs_time}%
\end{figure}

\begin{figure}%
%\includegraphics[width=\columnwidth]{case2_smoother_comparison_posRMSE_time-crop.pdf}%
\caption{RMSEs and running times of various smoothing algorithms}%
\label{fig:case2_rmse_vs_time}%
\end{figure}

@@

\appendices
\section{Appendix Title}
Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
\section{}
Appendix two text goes here.

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...

@@

\begin{IEEEbiography}{Pete Bunch}
Biography text here.
\end{IEEEbiography}

>>>>

%% Packages
\usepackage{cite}
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  \graphicspath{{../pdf/}{../jpeg/}}
  \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  \usepackage[dvips]{graphicx}
  \graphicspath{{../eps/}}
  \DeclareGraphicsExtensions{.eps}
\fi
\usepackage[cmex10]{amsmath}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{array}
\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{eqparbox}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{fixltx2e}
%\usepackage{stfloats}
\usepackage{url}

@@

% The paper headers
\markboth{IEEE Transaction in Signal Processing,~Vol.~1, No.~1, January~1901}%
{Bunch \& Godsill \MakeLowercase{\textit{et al.}}: Improved Particle Approximations to the Joint Smoothing Distribution Using Markov Chain Monte Carlo}

@@

\begin{IEEEeqnarray}{rCl}
p(x_{1:k}|\tilde{x}_{k+1}, y_{1:K}) & =       & p(x_{1:k}|\tilde{x}_{k+1}, y_{1:k}) \nonumber \\
                                    & \propto & p(\tilde{x}_{k+1}|x_k) p(x_k|x_{k-1}) p(y_k|x_x) p(x_{1:k-1}|y_{1:k-1})
\end{IEEEeqnarray}

@@

\begin{IEEEeqnarray}{rCl}
\underbrace{\begin{bmatrix}x_k \\ y_k \\ \dot{x}_k \\ \dot{y}_k\end{bmatrix}}_{\mathbf{x}_k} &=& \underbrace{\begin{bmatrix}I_2 & \Delta t I_2 \\ 0_2 & I_2\end{bmatrix}}_{\mathbf{A}} \underbrace{\begin{bmatrix}x_{k-1} \\ y_{k-1} \\ \dot{x}_{k-1} \\ \dot{y}_{k-1}\end{bmatrix}}_{\mathbf{x}_{k-1}} + \underbrace{\begin{bmatrix}w_{1,k} \\ w_{2,k} \\ w_{3,k} \\ w_{4,k}\end{bmatrix}}_{\mathbf{w}_k} \\
\underbrace{\begin{bmatrix}b_k \\ r_x\end{bmatrix}}_{\mathbf{y}_k} &=& \begin{bmatrix}\tan^{-1}(y_k / x_k) \\ \sqrt{x_k^2+y_k^2} \end{bmatrix} + \underbrace{\begin{bmatrix}v_{1,k} \\ v_{2,k}\end{bmatrix}}_{\mathbf{v}_k}
\end{IEEEeqnarray}

@@

\begin{figure}[!t]
\centerline{\subfloat[Case 1]{\includegraphics[width=0.45\columnwidth]{case1_trajectory-crop.pdf}%
\label{fig_first_case}}
\hfil
\subfloat[Case 2]{\includegraphics[width=0.45\columnwidth]{case2_trajectory-crop.pdf}%
\label{fig_second_case}}}
\caption{Example trajectory with observations from the two parameter cases.}
\label{fig:example_trajectories}
\end{figure}

@@

\begin{table}[!t]%
\renewcommand{\arraystretch}{1.3}
\caption{Smoother performance measures for parameter case 1. All results are averaged over 10 runs, with 500 time steps in each run.}
\label{tab:case1_performance}
\centering
\begin{tabular}{|c||c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{1cm} Postion RMSE \end{minipage} & \begin{minipage}[c]{1cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{1cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{1cm}  Unique Particles \end{minipage} \\
\hline
FS 						& 0.578 & 0.968 & 0 & 2.25 \\
DBRS					& 0.475 & 0.762 & 122 & 20.3 \\
\hline
MCMC-BRS (1)	& 0.509 & 0.823 & 3 & 13.7 \\
MCMC-BRS (3)	& 0.493 & 0.790 & 7 & 17.4 \\
MCMC-BRS (10)	& 0.482 & 0.768 & 21 & 19.6 \\
MCMC-BRS (30)	& 0.480 & 0.761 & 62 & 20.2 \\
MCMC-BRS (100)& 0.476 & 0.764 & 202 & 20.4 \\
\hline
MCMC-BSS (1)	& 0.473 & 0.758 & 14 & 44.3 \\
MCMC-BSS (3)	& 0.461 & 0.734 & 29 & 69.7 \\
MCMC-BSS (10)	& 0.451 & 0.720 & 82 & 89.8 \\
MCMC-BSS (30)	& 0.444 & 0.713 & 232 & 96.7 \\
MCMC-BSS (100)& 0.443 & 0.709 & 755 & 98.6 \\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]%
\renewcommand{\arraystretch}{1.3}
\caption{Smoother performance measures for parameter case 2. All results are averaged over 10 runs, with 500 time steps in each run.}
\label{tab:case2_performance}
\centering
\begin{tabular}{|c||c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{1cm} Postion RMSE \end{minipage} & \begin{minipage}[c]{1cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{1cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{1cm}  Unique Particles \end{minipage} \\
\hline
FS 						& 6.17 & 2.03 & 0 & 3.96 \\
DBRS					& 5.79 & 1.89 & 63 & 7.34 \\
\hline
MCMC-BRS (1)	& 6.13 & 2.01 & 2 & 4.77 \\
MCMC-BRS (3)	& 6.07 & 1.99 & 4 & 5.29 \\
MCMC-BRS (10)	& 5.94 & 1.94 & 10 & 6.1 \\
MCMC-BRS (30)	& 5.82 & 1.91 & 29 & 6.73 \\
MCMC-BRS (100)& 5.80 & 1.89 & 95 & 7.38 \\
\hline
MCMC-BSS (1)	& 5.90 & 1.91 & 9 & 12.6 \\
MCMC-BSS (3)	& 5.67 & 1.81 & 18 & 22.7 \\
MCMC-BSS (10)	& 5.48 & 1.73 & 50 & 44.1 \\
MCMC-BSS (30)	& 5.43 & 1.69 & 144 & 70.9 \\
MCMC-BSS (100)& 5.34 & 1.68 & 471 & 91.8 \\
\hline
\end{tabular}
\end{table}

\begin{figure}[!t]
\centering
\includegraphics[width=0.8\columnwidth]{case1_smoother_comparison_posRMSE_time-crop.pdf}%
\caption{RMSEs and running times of various smoothing algorithms}%
\label{fig:case1_rmse_vs_time}%
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=0.8\columnwidth]{case2_smoother_comparison_posRMSE_time-crop.pdf}%
\caption{RMSEs and running times of various smoothing algorithms}%
\label{fig:case2_rmse_vs_time}%
\end{figure}

@@

%\appendices
%\section{Appendix Title}
%Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
%\section{}
%Appendix two text goes here.

% use section* for acknowledgement
%\section*{Acknowledgment}

%The authors would like to thank...

@@

\begin{IEEEbiographynophoto}{Pete Bunch}
Biography text here.
\end{IEEEbiographynophoto}
